Table \ref{tab:table2changesinterview} replicates Panel A of Table 2 in Parker et al. 
Our sample size is little bit smaller (17,234 vs 17,478). But the estimates and standard errors are very similar.

Table \ref{tab:table2changesinterviewrbtonly} replicates Panel B of Table 2 in Parker et al. 
Again, the estimates and standard errors are very similar.

Tables \ref{tab:table2changesinterviewlags} and \ref{tab:table2changesinterviewrbtonlylags} 
add a single lag to the result as this leaves the sample size unaffected. 
There is some uncertainty around whether the spending changes are persistent.
In general, the level specification imply more persistence than the log specification,
and the interview sample implies more persistence than the full sample.

Tables \ref{tab:table2levelinterview} through \ref{tab:table2levelinterviewrbtonlylags} 
repeat the same estimation but with the dependent variable in levels rather than in
changes. We also add a household fixed effect to the estimation. The overall estimates
for spending effects are similar to the regressions in changes. The level specifications
more consistently point towards a transitory effect of the rebate on spending. The level
specifications are also less sensitive to the sample.


Tables \ref{tab:table2changesmonthly} through \ref{tab:table2levelmonthlyrbtonlylags} 
conduct the entire analysis at the monthly frequency. The rebate vairbale is
now the month in which the rebate is received.

\begin{landscape}
\input{./tables/table2changesinterview.tex}
\input{./tables/table2changesinterviewrbtonly.tex}
\input{./tables/table2changesinterviewlags.tex}
\input{./tables/table2changesinterviewrbtonlylags.tex}

\input{./tables/table2levelinterview.tex}
\input{./tables/table2levelinterviewrbtonly.tex}
\input{./tables/table2levelinterviewlags.tex}
\input{./tables/table2levelinterviewrbtonlylags.tex}

\input{./tables/table2changesmonthly.tex}
\input{./tables/table2changesmonthlyrbtonly.tex}
\input{./tables/table2changesmonthlylags.tex}
\input{./tables/table2changesmonthlyrbtonlylags.tex}

\input{./tables/table2levelmonthly.tex}
\input{./tables/table2levelmonthlyrbtonly.tex}
\input{./tables/table2levelmonthlylags.tex}
\input{./tables/table2levelmonthlyrbtonlylags.tex}

% \input{./tables/table2d_foodbevs}
% \input{./tables/table2d_sndexp}
% \input{./tables/table2d_ndexp}
% \input{./tables/table2d_totexp2}

% \input{./tables/table2foodbevs}
% \input{./tables/table2sndexp}
% \input{./tables/table2ndexp}
% \input{./tables/table2totexp2}

\end{landscape}